---
title: "README"
author: "Shan Luo"
date: "2022-07-29"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Brief description of the app and its purpose.  

This app allows user to visualize the data, fit three different model with different variables, obtain the prediction from model, and subset the original data.  
There are five predictors and one binary response from [Heart Failure Prediction Dataset](https://www.kaggle.com/datasets/fedesoriano/heart-failure-prediction).  

The purpose is to allow me to utilize the knowledge about Shiny App.  

# Package Lists
[`shinydashboard`](https://cran.r-project.org/web/packages/shinydashboard/index.html)  
[`shiny`](https://cran.r-project.org/web/packages/shiny/index.html)  
[`tidyverse`](https://www.tidyverse.org/)  
[`DT`](https://www.rdocumentation.org/packages/DT/versions/0.16)  
[`ggplot2`](https://ggplot2.tidyverse.org)  
[`recipes`](https://cran.r-project.org/web/packages/recipes/index.html)  
[`caret`](https://topepo.github.io/caret/)  

# Install Package Lists
```{r install Package, echo=TRUE, eval=FALSE}
install.packages(c("shinydashboard", "shiny", "tidyverse",
                   "DT", "ggplot2", "recipes", "caret"))
```

# Run App
```{r runapp, echo=TRUE, eval=FALSE}
shiny::runGitHub(repo = "ST558Project3", username = "ShanLLL52")
```

# Code for Render README
```{r README, echo=TRUE, eval=FALSE}
rmarkdown::render("README.Rmd", 
          output_format = "github_document",
          output_file = "README.md",
          output_options = list(
            html_preview = FALSE))
```

